---
title: "Stats_Final_Proj"
output: pdf_document
---

```{r}
#rm(list=ls()); gc()  # Cleanup

library(tidyverse)
library(reshape2)
library(xts)
library(lubridate)
library(data.table)
library(highcharter)  # If you haven't used this charting package before, get the latest from CRAN: install.packages("highcharter")

options(tibble.width = Inf)  # Prints all columns in a tibble in the console

```

## Load data from csv
```{r}
contacts <- read_csv('contacts.csv')
listings <- read_csv('listings.csv')
users <- read_csv('users.csv')
```

## Join all 3 together into 1 giant master table:
```{r}
co <- left_join(left_join(left_join(contacts, listings), users, by = c("id_guest_anon" = "id_user_anon")), users, by = c("id_host_anon" = "id_user_anon"), suffix = c("_guest", "_host")) %>% distinct() %>%  # Remove duplicates
filter(guest_user_stage_first != '-unknown-' & total_reviews >= 0 & (ts_booking_at <= ds_checkout_first | is.na(ts_booking_at)))  # Assume rows where user's first stage is unknown or review count is negative as junk data; also, you can't confirm a booking beyond the checkout date (that wouldn't make sense)

```

## Create data.frames/tibbles:
```{r}
co <- left_join(
  left_join(
    left_join(co, listings), users, by = c("id_guest_anon" = "id_user_anon")), users, by = c("id_host_anon" = "id_user_anon"), suffix = c("_guest", "_host")) %>%
  distinct() %>%  # Remove duplicates
  filter(guest_user_stage_first != '-unknown-' & total_reviews >= 0 & (ts_booking_at <= ds_checkout_first | is.na(ts_booking_at)))  # Assume rows where user's first stage is unknown or review count is negative as junk data; also, you can't confirm a booking beyond the checkout date (that wouldn't make sense)

```

```{r}
# List of counts of interactions/replies/acceptances/bookings & proportions, aggregated by month, segmented by contact channel:
contacts_monthly <- sapply(X = c("contact_me", "book_it", "instant_book"), FUN = function(x) {
  foo <- co %>%
    filter(contact_channel_first == x) %>%
    mutate(ds_interaction_first = floor_date(ts_interaction_first, "month")) %>%  # group by month starting
    group_by(ds_interaction_first) %>%
    summarise(interactions = length(ts_interaction_first),
              replies = sum(!is.na(ts_reply_at_first)),
              acceptances = sum(!is.na(ts_accepted_at_first)),
              bookings = sum(!is.na(ts_booking_at))) %>%
    mutate(reply_rate = replies/interactions,
           accept_rate = acceptances/interactions,
           booking_rate = bookings/interactions,
           abandon_rate = accept_rate-booking_rate) %>%
    as.data.frame()
  return(xts(foo[-1], order.by = as.Date(foo[,1])))  # Convert to `xts` class time-series object
}, simplify = F)  # names(contacts_monthly)

```

```{r}
# Time (hours) in-between funnel stages, segmented by new/existing customer & contact channel:
new_v_past_by_channel <- co %>% 
  mutate(time_interaction_to_reply = difftime(ts_reply_at_first, ts_interaction_first, units = "hours"),
         time_reply_to_accept = difftime(ts_accepted_at_first, ts_reply_at_first, units = "hours"),
         time_accept_to_book = difftime(ts_booking_at, ts_accepted_at_first, units = "hours"),
         start_to_finish = difftime(ts_booking_at, ts_reply_at_first, units = "hours")) %>%  # Total time in the funnel
  group_by(guest_user_stage_first, contact_channel_first) %>%
  summarise(avg_time_interaction_to_reply = round(mean(time_interaction_to_reply, na.rm = T), 2),
            avg_time_reply_to_accept = round(mean(time_reply_to_accept, na.rm = T), 2),
            avg_time_accept_to_book = round(mean(time_accept_to_book, na.rm = T), 2),
            avg_start_to_finish = round(mean(start_to_finish, na.rm = T), 2))

```

```{r}
# List of flattened contacts with additional explanatory 0/1 variables for further manipulation:
contacts_flat <- sapply(X = c("contact_me", "book_it"), FUN = function(x) {co %>% 
    mutate(length_of_stay_days = as.integer(difftime(ds_checkout_first, ds_checkin_first, units = "days")),
           replied = case_when(
             !is.na(ts_reply_at_first) ~ 1,
             TRUE ~ 0
           ),
           accepted = case_when(
             !is.na(ts_accepted_at_first) ~ 1,
             TRUE ~ 0
           ),
           booked = case_when(
             !is.na(ts_booking_at) ~ 1,
             TRUE ~ 0
           ),
           guest_host_same_country = case_when(
             country_guest == country_host ~ 1,
             TRUE ~ 0
           ),
           neighborhood_listed = case_when(
             listing_neighborhood == "-unknown-" ~ 0,
             TRUE ~ 1
           ),
           guest_profile_words = case_when(
             words_in_user_profile_guest <= 3 ~ "3 words or less",
             TRUE ~ "More than 3 words"
           ),
           host_profile_words = case_when(
             words_in_user_profile_host <= 3 ~ "3 words or less",
             TRUE ~ "More than 3 words"
           )) %>%
    filter(contact_channel_first == x) %>%
    dplyr::select(contact_channel_first, 
           guest_user_stage_first, 
           m_guests, m_interactions, 
           m_first_message_length_in_characters, 
           length_of_stay_days, 
           room_type,
           total_reviews,
           listing_neighborhood,
           neighborhood_listed,
           guest_host_same_country,
           words_in_user_profile_guest,
           words_in_user_profile_host,
           guest_profile_words,
           host_profile_words,
           replied, 
           accepted, 
           booked)
}, simplify = F)
```

## Charts
```{r}
# Booking "funnel" for 3 channels:
highchart(type = "stock") %>%
  hc_title(text = "Contact Me vs. Book It vs. Instant") %>%
  hc_subtitle(text = "Monthly Interactions / Replies / Acceptances / Bookings") %>%
  hc_yAxis_multiples(
    create_yaxis(3, height = c(1, 1, 1), turnopposite = TRUE)
  ) %>%
  hc_add_series(contacts_monthly[["contact_me"]][,c("interactions")], yAxis = 0, name = "Contact Me - # Interactions", type = "column", color = "#e91e63") %>%
  hc_add_series(contacts_monthly[["contact_me"]][,c("replies")], yAxis = 0, name = "Contact Me - # Replies", type = "column", color = "#c2185b") %>%
  hc_add_series(contacts_monthly[["contact_me"]][,c("acceptances")], yAxis = 0, name = "Contact Me - # Acceptances", type = "column", color = "#3f51b5") %>%
  hc_add_series(contacts_monthly[["contact_me"]][,c("bookings")], yAxis = 0, name = "Contact Me - # Bookings", type = "column", color = "#2196f3") %>%

  hc_add_series(contacts_monthly[["book_it"]][,c("interactions")], yAxis = 1, name = "Book It - # Interactions", type = "column", color = "#e91e63") %>%
  hc_add_series(contacts_monthly[["book_it"]][,c("replies")], yAxis = 1, name = "Book It - # Replies", type = "column", color = "#c2185b") %>%
  hc_add_series(contacts_monthly[["book_it"]][,c("acceptances")], yAxis = 1, name = "Book It - # Acceptances", type = "column", color = "#3f51b5") %>%
  hc_add_series(contacts_monthly[["book_it"]][,c("bookings")], yAxis = 1, name = "Book It - # Bookings", type = "column", color = "#2196f3") %>%
  
  hc_add_series(contacts_monthly[["instant_book"]][,c("bookings")], yAxis = 2, name = "Instant - # Bookings", type = "column", color = "#2196f3")

```

- Notes on above: "Contact Me" channel has massive drop-off at last stage of the funnel, that is where a booking was accepted, but didn't end up getting booked (abandoned).
- Opportunity exists to increase bookings by reducing the drop-off at the Reply >> Acceptance & Acceptance >> Booking stages of the booking funnel.

```{r}
# Reply/Acceptance/Booking/Abandon rates for Contact Me vs. Book It:
highchart(type = "stock") %>%
  hc_title(text = "Contact Me vs. Book It") %>%
  hc_subtitle(text = "Monthly Reply / Acceptance / Booking / Abandonment Rates") %>%
  hc_yAxis_multiples(
    create_yaxis(2, height = c(1, 1), turnopposite = TRUE)
  ) %>%
  hc_add_series(round(contacts_monthly[["contact_me"]][,c("reply_rate")], 3), yAxis = 0, name = "Contact Me - Reply %", type = "column", color = "#673ab7") %>%
  hc_add_series(round(contacts_monthly[["contact_me"]][,c("accept_rate")], 3), yAxis = 0, name = "Contact Me - Accept %", type = "column", color = "#3f51b5") %>%
  hc_add_series(round(contacts_monthly[["contact_me"]][,c("booking_rate")], 3), yAxis = 0, name = "Contact Me - Booking %", type = "column", color = "#2196f3") %>%
  hc_add_series(round(contacts_monthly[["contact_me"]][,c("abandon_rate")], 3), yAxis = 0, name = "Contact Me - Abandon %", type = "column", color = "#f44336") %>%
  
  hc_add_series(round(contacts_monthly[["book_it"]][,c("reply_rate")], 3), yAxis = 1, name = "Book It - Reply %", type = "column", color = "#673ab7") %>%
  hc_add_series(round(contacts_monthly[["book_it"]][,c("accept_rate")], 3), yAxis = 1, name = "Book It - Accept %", type = "column", color = "#3f51b5") %>%
  hc_add_series(round(contacts_monthly[["book_it"]][,c("booking_rate")], 3), yAxis = 1, name = "Book It - Booking %", type = "column", color = "#2196f3") %>%
  hc_add_series(round(contacts_monthly[["book_it"]][,c("abandon_rate")], 3), yAxis = 1, name = "Book It - Abandon %", type = "column", color = "#f44336")

```

- Notes on above: As we saw in the first chart, the abandon rate for the "Contact Me" channel is super-high (10X the same metric for "Book It").
- Also, there's a near 40% drop-off between the reply >> acceptance stages, suggesting there's an opportunity to increase total bookings if we can close this gap.

```{r}
# Average hours in-between:
reshape2::melt(as.data.frame(new_v_past_by_channel)) %>%
  filter(guest_user_stage_first == "new" & contact_channel_first != "instant_book") %>%  # Ignore Instant bookings since there is not any time in-between stages
  hchart("column", hcaes(x = "variable", y = "value", group = "contact_channel_first")) %>%
  hc_title(text = "New Bookers") %>%
  hc_subtitle(text = "Average Hours In-between") %>%
  hc_xAxis(title = NULL, categories = list("Interaction-to-Reply", "Reply-to-Accept", "Accept-to-Book", "Start-to-Finish")) %>%
  hc_yAxis(title = list(text = "Time (Hours)"))
  
reshape2::melt(as.data.frame(new_v_past_by_channel)) %>%
  filter(guest_user_stage_first == "past_booker" & contact_channel_first != "instant_book") %>%
  hchart("column", hcaes(x = "variable", y = "value", group = "contact_channel_first")) %>%
  hc_title(text = "Past Bookers") %>%
  hc_subtitle(text = "Average Hours In-between") %>%
  hc_xAxis(title = NULL, categories = list("Interaction-to-Reply", "Reply-to-Accept", "Accept-to-Book", "Start-to-Finish")) %>%
  hc_yAxis(title = list(text = "Time (Hours)"))

```

- Notes on above: We see in the above that, for new/past bookers alike, the average time it takes from initial contact to 1st reply for the "Contact Me" channel is MUCH slower than "Book It".
- From a customer experience perspective, this is a clear negative as when searching for travel acccommodations, one would intuitively prefer speed. For new customers especially, having to wait upwards of a day (on average) to get a response is simply unacceptable -- why not just book a hotel?
- Also, bookers using "Contact Me" are waiting a *VERY* long time after their bookings are accepted to actually book. Possible reason: users are shopping around for other listings or simply indecisive.
- Lastly, the total time spent in the funnel from first interaction to booking for "Contact Me" is 9-10x longer than "Book It" (which, on average, is within a half-day). This suggests a bad customer experience--nobody wants to spend *days* waiting around to book travel accommodations.

- Above we've seen that the "Contact Me" channel is clearly performing badly, and the obvious recommendation would be to nix it in favor of going "Book it" and "Instant Book" only.
- However, what if an Airbnb product manager said "Nah, we're keeping 'Contact Me' no matter what." What then?
- Well, the goal then would be to seek out ways to improve conversion @ various stages of the funnel, which in turn would [hopefully] drive additional bookings/increased conversion.
  
- Let's consider a few ideas at a couple different stages of the funnel.

## Q: If we use the # of interactions a proxy for how "active" guests/hosts are in comms, does this have an effect on reply/accept/booking rate?

- Intuitively, it follows that the more guests/hosts communicate with one another, the more comfortable they become and thus more likely to have an accepted/completed booking.

```{r}
hchart(contacts_flat[["contact_me"]][["m_interactions"]])  # Quick histogram of interaction count; observe, skewed fat left tail.
```

```{r}
# Create ordinal segmentation based on # of interactions according to: quantile(contacts_flat[["contact_me"]][["m_interactions"]])
n_interactions <- contacts_flat[["contact_me"]] %>%
  mutate(n_interaction_group = case_when(
    m_interactions > 0 & m_interactions <= 1 ~ "1 interaction",
    m_interactions > 1 & m_interactions <= 2 ~ "2 interactions",
    m_interactions > 2 & m_interactions <= 3 ~ "3 interactions",
    m_interactions > 3 & m_interactions <= 6 ~ "4-6 interactions",
    m_interactions > 6 ~ "7+ interactions"
  )) %>%
  group_by(n_interaction_group) %>%
  summarise(n = n(),
            replies = sum(replied),
            accepts = sum(accepted),
            bookings = sum(booked),
            reply_rate = sum(replied)/n(),
            accept_rate = sum(accepted)/n(),
            booking_rate = sum(booked)/n())

reshape2::melt(n_interactions[,c("n_interaction_group", "reply_rate", "accept_rate", "booking_rate")]) %>%
  hchart("bar", hcaes(x = "variable", y = "value", group = "n_interaction_group")) %>%
  hc_title(text = "Reply / Acceptance / Booking Rates") %>%
  hc_subtitle(text = "Segmented by # Total Interactions") %>%
  hc_xAxis(title = NULL, categories = list("Reply (%)", "Accept (%)", "Booking (%)")) %>%
  hc_yAxis(title = "Percentage (%)", max = 1)

```

## Q: Is the above statistically significant?

```{r}
prop.trend.test(n_interactions[["replies"]], n_interactions[["n"]])  # Use prop.trend.test() due to ordinal data
prop.trend.test(n_interactions[["accepts"]], n_interactions[["n"]])
prop.trend.test(n_interactions[["bookings"]], n_interactions[["n"]])

```

- Based on the above chart & statistical tests (p-value's < 2.2e-16 for all 3), we see that there does appear to be a positive relationship between Acceptance & Booking Rates, as the # of interactions increase.
- For those where there was only a *single* interaction (i.e. the potential guest sends the only message with no reply from the host), the Acceptance/Booking rates is understandbly very low.
- The obvious recommendation here would be to *REQUIRE* hosts to respond to the initial guest message to improve the guest customer experience; in general, you would want to encourage both guests/hosts to actively communicate with one another in the "Contact Me" feature flow, as that improves the likelihood of a successful booking.

## Q: Okay, so we see that active communication between guests/hosts plays a role in whether or not a booking gets accepted or ultimlately confirmed, but how can we drive that and encourage hosts to actually respond?

- Let's take a look at the length of *FIRST* communication! Intuitively, one might expect a longer first message is more likely to get a reply from host.
- Something like "Hi, my name is Ray" probably isn't going to garner much of a response from a potential host, but a longer message that introduces yourself and why you're visiting Rio de Janeiro probably would.

```{r}
hchart(contacts_flat[["contact_me"]][["m_first_message_length_in_characters"]])  # Quick histogram of initial message lengths  
```

Again, let's create ordinal segmentation based on the above:

```{r}
quantile(contacts_flat[["contact_me"]][["m_first_message_length_in_characters"]])  
```

```{r}
first_msg_length <- contacts_flat[["contact_me"]] %>%
  mutate(first_msg_nchar = case_when(
    m_first_message_length_in_characters >= 0 & m_first_message_length_in_characters < 107 ~ "0 - 106", # 25th percentile
    m_first_message_length_in_characters >= 107 & m_first_message_length_in_characters < 183 ~ "107 - 182",  # 50th percentile
    m_first_message_length_in_characters >= 183 & m_first_message_length_in_characters < 301 ~ "183 - 300",  # 75th percentile
    m_first_message_length_in_characters >= 301 ~ "300+"
  )) %>%
  group_by(first_msg_nchar) %>%
  summarise(n = n(),
    replies = sum(replied),
    accepts = sum(accepted),
    reply_rate = sum(replied)/n(),
    accept_rate = sum(accepts)/n())

```

```{r}
# Chart it:
reshape2::melt(first_msg_length[,c("first_msg_nchar", "reply_rate", "accept_rate")]) %>%
  hchart("bar", hcaes(x = "variable", y = "value", group = "first_msg_nchar")) %>%
  hc_title(text = "Reply / Acceptance Rates") %>%
  hc_subtitle(text = "Segmented by # Characters in Guest's Initial Message") %>%
  hc_xAxis(title = NULL, categories = list("Reply (%)","Accept (%)")) %>%
  hc_yAxis(title = "Percentage (%)", max = 1)

```

```{r}
# Again, let's compute multi-proportion Chi-squared test statistic:
prop.trend.test(first_msg_length[["replies"]], first_msg_length[["n"]])  # p-value = 0.01428
prop.trend.test(first_msg_length[["accepts"]], first_msg_length[["n"]])  # p-value = 0.008349
prop.test(c(sum(first_msg_length[["replies"]][1:2]), sum(first_msg_length[["replies"]][3:4])), c(sum(first_msg_length[["n"]][1:2]), sum(first_msg_length[["n"]][3:4]))) # Also do it for two groups @ the 50th percentile
# returns: p-value = 0.01714
prop.test(c(sum(first_msg_length[["accepts"]][1:2]), sum(first_msg_length[["accepts"]][3:4])), c(sum(first_msg_length[["n"]][1:2]), sum(first_msg_length[["n"]][3:4]))) # Also do it for two groups @ the 50th percentile
# returns: p-value = 0.01621

```
- Based on the above, we reject the null hypothesis with 95% confidence; that is, there *is* a statistically significant relationship between the length of a guest's initial message and the likelihood of a reply, and ultimately accepted booking under the "Contact Me" feature flow.
- Even though the difference *seems* small (~ 1-2% in reply rate; ~2-3% in acceptance), the p-value's being < 0.02 confirm this is something we shouldn't overlook.
- Recommendation: If we continue with the "Contact Me" flow, require potential guests to write an introductory message longer than approx. 180 characters -- which to be fair, isn't much longer than a Tweet.
- This makes for a better host experience as one might want to know a little bit more about who is staying in their listing before accepting their request.

## Cumulative count of new/past bookers, over time:

```{r}

new_vs_past <- co %>%
  mutate(ds_interaction_first = floor_date(ts_interaction_first, "day")) %>%
  group_by(ds_interaction_first) %>%
  summarise(n_guest = n_distinct(id_guest_anon),
    n_new = data.table::uniqueN(id_guest_anon[guest_user_stage_first == "new" ]),
    n_past = data.table::uniqueN(id_guest_anon[guest_user_stage_first == "past_booker"])) %>%
  mutate(pct_new = n_new/n_guest, pct_past = n_past/n_guest, cum_n_new = cumsum(n_new), cum_n_past = cumsum(n_past), cum_pct_new = cumsum(n_new)/cumsum(n_guest), cum_pct_past = cumsum(n_past)/cumsum(n_guest)) %>%
  as.data.frame()

new_vs_past.xts <- xts(new_vs_past[-1], order.by = as.Date(new_vs_past[,1]))

highchart(type = "stock") %>%
  hc_title(text = "Daily New vs. Past Bookers") %>%
  hc_yAxis_multiples(
    create_yaxis(3, height = c(1, 1, 1), turnopposite = TRUE)
  ) %>%
hc_add_series(new_vs_past.xts[,c("n_new")], yAxis = 0, name = "# New", type = "line", color = "#e91e63") %>%
  hc_add_series(new_vs_past.xts[,c("n_past")], yAxis = 0, name = "# Past", type = "line", color = "#3f51b5") %>%
  
  hc_add_series(new_vs_past.xts[,c("cum_n_new")], yAxis = 1, name = "# New (Cumulative)", type = "line", color = "#e91e63") %>%
  hc_add_series(new_vs_past.xts[,c("cum_n_past")], yAxis = 1, name = "# Past (Cumulative)", type = "line", color = "#3f51b5") %>%
  
  hc_add_series(new_vs_past.xts[,c("cum_pct_new")], yAxis = 2, name = "% New (Cumulative)", type = "line", color = "#e91e63") %>%
  hc_add_series(new_vs_past.xts[,c("cum_pct_past")], yAxis = 2, name = "% Past (Cumulative)", type = "line", color = "#3f51b5")

# **Notes on above**: The cumulative # of new & past users is growing linearly since 1/1/16 (Q: did Airbnb guys launch RDJ in Jan'16? There's a spike in the beginning); the former is growing at a faster rate, and the latter isn't plateauing--these both suggest a healthy market.
# There also aren't any abnormal spikes in the data as well (good thing) and the cumulative split % between new/past is stabilizing, but not converging. Convergence would probably be a bad sign as you want continuous growth; cum % existing customers shouldn't overtake news ones would mean stalling new customer acquisition.
```

## Q: Does the neighborhood, known or unknown, make a guest more likely to book?

```{r}
contacts_flat[["contact_me"]] %>%
  group_by(neighborhood_listed) %>%
  summarise(n = n(),
    accepts = sum(accepted),
    bookings = sum(booked),
    abandons = sum(accepted)-sum(booked),
    accept_rate = sum(accepted)/n(),
    booking_rate = sum(booked)/n(),
    abandon_rate = (sum(accepted)-sum(booked))/n()
  ) %>%
  arrange(desc(n))
```

## Quick 2 sample Z-test on booking rates where neighborhood is listed (or not)
```{r}
prop.test(x = c(524, 377), n = c(6850,  5919), alternative = "two.sided")  
```
- p-value of 0.005394, thus we reject H0 with 95% confidence; that is, there is statistical significance in booking rate when neighborhood is/isn't listed


***************************************************************************
### Statistical Analysis ###
***************************************************************************
```{r echo = FALSE, eval= TRUE}
contacts<- left_join(left_join(left_join(contacts, listings), users, by = c("id_guest_anon" = "id_user_anon")), users, by = c("id_host_anon" = "id_user_anon"), suffix = c("_guest", "_host")) %>% distinct() %>%  # Remove duplicates
filter(guest_user_stage_first != '-unknown-' & total_reviews >= 0 & (ts_booking_at <= ds_checkout_first | is.na(ts_booking_at)))
```

Significance level = 5%

**1. Is the average number of interactions equal in inquiries by past bookers and new guests? (Welch t-test for equal means) **

```{r echo=F, eval=T}
past_bookers = contacts[contacts$guest_user_stage_first=="past_booker",]
n_past_bookers = nrow(past_bookers)

new_guests = contacts[contacts$guest_user_stage_first=="new",]
n_new_guests = nrow(new_guests)
```

\(H_{0}\) : Mean number of interactions of past bookers is equal to or less than new guests

\(H_{A}\) : Mean number of interactions of past bookers is more than new guests


```{r echo=F, eval=T}
t.test(past_bookers$m_interactions,new_guests$m_interactions, var.equal=F,alt="greater")
```

* Since p-value is less than 0.05, we can conclude that mean number of interactions of past bookers is more.

* Also, the 95% confidence interval of difference does not include 0.

**2. Is the median number of interactions equal in inquiries by past bookers and new guests? (Wilcoxon Rank Sum Test) **

\(H_{0}\) : Median number of interactions of past bookers is equal to or less than new guests

\(H_{A}\) : Median number of interactions of past bookers is more than new guests

```{r echo=F, eval=T}
wilcox.test(past_bookers$m_interactions,new_guests$m_interactions,exact=F,correct=F,conf.int=T,alt="greater")
```

* Since p-value is less than 0.05, we can conclude that median number of interactions of past bookers is more.

* Also, the 95% confidence interval of difference does not include 0.

* From Parts 1 & 2, we see that past bookers interact more with the hosts.

**3. We have a hunch that over half of the guests who instantly book properties are confident past bookers? Is this true? (Z-test for proportion) **

\(H_{0}\) : p \(\leq\) 0.5

\(H_{A}\) : p \(>\) 0.5

```{r echo=F, eval=T}
instant_book = contacts[contacts$contact_channel_first=="instant_book",]
past_instant_book = instant_book[instant_book$guest_user_stage_first=="past_booker",]

prop.test(x=nrow(past_instant_book), n=nrow(instant_book), p = 0.5, alternative = "greater", correct = TRUE)
```

* Since p-value is more than 0.05, we can conclude that more than half of instant bookings are from past bookers.

* We are 95% confident that proportion of instant bookings done by past bookers is in [0.57, 1]

**4. Are contact channel and guest user stage (new or past booker) independent? In other words, do new guests display any preference in their inquiries? (Chi-square test for independence)**

\(H_{0}\) : Contact channel and guest user stage are independent

\(H_{A}\) : Contact channel and guest user stage are associated

```{r echo=F, eval=T}
notunknown = contacts[contacts$guest_user_stage_first!="-unknown-",]
observed = table(notunknown$contact_channel_first, notunknown$guest_user_stage_first)
observed

chisq.test(observed, correct=F)
```

Since p-value is less than 0.05, we can conclude that there is an associate between contact channel and guest user stage.

**5. Can we linearly predict the number of guests based on other request details? It is possible that guests who have a large booking are more likely to interact with the hosts. Are large booking requests (higher number of guests) associated with higher number of interactions? (Correlation and Regression)**

```{r echo=F, eval=T}
cor.test(contacts$m_interactions, contacts$m_guests)
```

Correlation between number of interactions and number of guests = -0.03656

```{r echo=F, eval=T}
cor.test(contacts$m_first_message_length_in_characters, contacts$m_guests)
```

Correlation between length of first message and number of guests = -0.02791

Both the correlations are significant

```{r echo=F, eval=T}
xbar_int = mean(contacts$m_guests,na.rm=T)
plot(1:length(contacts$m_guests), contacts$m_interactions, main="Incomes",
   xlab="Values", ylab="Number of Interactions", pch=19)
abline(a=xbar_int, b=0, col='blue')

xbar_ml = mean(contacts$m_first_message_length_in_characters,na.rm=T)
plot(1:length(contacts$m_guests), contacts$m_first_message_length_in_characters, main="Age",
   xlab="Values", ylab="First message length", pch=19)
abline(a=xbar_ml, b=0, col='blue')
```

Number of interactions and first message length (the two numeric variables) have a constant variance and this meets the homoscedasticity assumption. 

```{r echo=F, eval=T}
boxplot(contacts$m_guests ~ contacts$contact_channel_first, main="Distribution of guests per channel", ylab="Number of guests", xlab="Contact channel") 

boxplot(contacts$m_guests ~ contacts$guest_user_stage_first, main="Distribution of guests per stage", ylab="Number of guests", xlab="User stage") 
```

Neither the categorical nor the numeric variables indicate an association. 

```{r echo=F, eval=T}
fit=lm(contacts$m_guests~contacts$m_interactions+contacts$m_first_message_length_in_characters+contacts$contact_channel_first+contacts$guest_user_stage_first)
summary(fit)
```

A linear regression model thus fails to model the number of guests based on inquiry details.

**6. Is the average number of guests equal in inquiries across all contact channels? (One-way ANOVA)**

\(H_{0}\) : Mean number of guests is equal for book it, contact me and instant book channels

\(H_{A}\) : At least one of the the means differs from one of the others

```{r echo=F, eval=T}
fit=aov(contacts$m_guests~contacts$contact_channel_first)
summary(fit)
anova(fit)
```

Since p-value is less than 0.05, mean number of guests is not equal across channels.


